\hiddenchapter {{\large{S}YSTEM ANALYSIS }}
\ChapterTitle [\thechapter]{SYSTEM  ANALYSIS }

\hiddensection{{\large{S}}YSTEM FUNCTIONAL REQUIREMENTS}
\SectionTitle{\thesection}{SYSTEM FUNCTIONAL REQUIREMENTS}
 
 \subsection{Authentication}
   \begin{itemize}
       \item R1. The user shall be able to log in or sign up.
   \end{itemize}

\subsection{Query Input \& Document Management}
   \begin{itemize}
       \item R2. The user shall be able to input keywords, topics, or research questions.
       \item R3. The user shall submit the input using a "Send" button.
       \item R4. The system shall display a ranked list of similar documents with metadata (title, author, etc.).
       \item R5. The user shall be able to navigate the list or skip it entirely.
       \item R6. The user shall be able to discard documents, leaving at least one selected.
       \item R7. The user shall be able to upload a PDF to customize the document set.
       \item R8. The user shall be able to save the selected documents and proceed.
   \end{itemize}

\subsection{Initial Chatbot}
   \begin{itemize}
       \item R: Once the user saved the documents, the user shall see a chatbot interface to chat about the scientific terminology
       \item R: The User shall see buttons representing the actions such as (Chat    Generate Knowledge Graph)
   \end{itemize}

\subsection{Knowledge Graph}
   \begin{itemize}
       \item R9. The system shall generate a knowledge graph where the user’s topic is the highlighted main node.
       \item R10. Hovering an ancestor node shall highlight it and its relation to the main topic.
       \item R11. Hovering a descendant node shall highlight it and its dependency on the main topic.
       \item R12. Other nodes shall be displayed farther away to indicate looser relations.
       \item R13. The user shall be able to click any node to open detailed content.
   \end{itemize}

\subsection{Explanation \& Chat}
   \begin{itemize}
       \item R14. When a node is clicked, the system shall generate a scientific explanation in a chat interface.
       \item R15. The generated explanation shall include backlinks to all ancestor and descendant nodes relevant to it.
       \item R16. The chat shall be saved automatically.
   \end{itemize}


\subsection{Side Notebook}
\begin{itemize}
    \item    R17. The user shall be able to open an optional side notebook alongside the chat.
    \item    R18. The user shall be able to add selected chat content to the notebook in structured format.
    \item    R19. The user shall be able to request “Summarize and Add to Notebook.”
    \item    R20. The user shall be able to freely edit the notebook.
    \item    R21. The user shall enable or disable automatic backlink generation in the notebook.
\end{itemize}


\subsection{Project Management}
   \begin{itemize}
       \item R22. Graphs, chats, and notebooks shall be stored together as a research project with an editable name.
       \item R23. The user shall be able to track references for each generated explanation.
   \end{itemize}

\clearpage